A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-11-12 writedown/zm/paper.water/main.tex
small revise...
revise by Fukuda

%2multibyte Version: 5.50.0.2952 CodePage: 932
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
%\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}

@@

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2952}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Friday, November 07, 2014 19:42:26}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}
% \input{tcilatex}
\begin{document}

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}

@@

{\color{red} If we want to discuss the issue of cut-off method, a short
introduction of the group cut-off v.s.~the atom cut-off method. (will
discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
do you mean? \recheck{I mean the explanation of group and atomistic cut-off method. the traditional gromacs uses gropu cut-off as default. We need instead the atomistic cut-off}}]

@@

\subsection{Simulation protocols}
\label{sec:protocols}
In this work, we focus on a system of water molecules modeled
by TIP3P~\cite{jorgensen1983comparison} point-charge particles. 
% Other point-charge water models differ in the modeling parameters, and
The accuracy of ZM method in other water models is out of the scope of the
current work. However, since the point-charge water models share similar
idea, and only differ in the model parameters, it is highly probable that ZM
works well with other water models if it works well with TIP3P.

@@

The neighbor lists were updated every 5 time-steps. The \textquotedblleft 
\texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used. In
order to mimic the atomistic cut-off manner, the radius for neighbor list
building was set 0.3~nm larger than the cut-off radius (the maximum of
Coulomb cut-off and the van der Waals cut-off). [ {\color{blue} COMMENT:
Yes,..., this is not easy to understand how we mimic AC. \recheck{it should be OK as it is now.}}] To make sure the
van der Waals interactions were cut-off in a smooth way, they are modified
in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs
\textquotedblleft \texttt{shift}\textquotedblright\ method.

The short-range part of SPME method \recheck{was cut-offed at 1.9~nm, and was} smoothed in a shell of $0.05$~nm
width by the Gromacs \textquotedblleft \texttt{pme-switch}%
\textquotedblright\ method. The reciprocal space grid spacing was set to
0.06~nm, with B-Spline interpolation order of 6. These parameters were
chosen to be more accurate than the Gromacs default choices (grid spacing
0.12~nm and interpolation order 4). The splitting parameter was optimized by
the error estimate for the SPME method, which is implemented in Gromacs by
tool \textquotedblleft \texttt{g\_pme\_error}\textquotedblright ~\cite%
{wang2010optimizing}. The optimized real space and reciprocal space force
computing errors were equally distributed as $1.4\times 10^{-4}$~kJ/(mol
nm). Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm),
this force computing precision almost reaches the limit of the
single-precision representation of the floating point numbers.

In the simulations of the RF method, the interactions were cut-off in the
group manner, so the radius for neighbor list building is set identical to
the cut-off radius. No cut-off smoothing of the electrostatic interaction
was applied in the cases of RF simulations. We used $1.2$~nm
cut-off and the experimental dielectric constant $\varepsilon _{\textrm{rf}}=80$.

The ZM method was implemented in Gromacs with the tabulated electrostatic
interaction. A home-made code was used to generate the interaction tables.

@@

The initial configurations were prepared by in the following steps: (1) An
NPT simulation of system $L_{0}$ with SPME electrostatic was performed. The
equilibrium density (984.1~$\text{kg}/\text{m}^{3}$) of the system is
calculated from this simulation. (2) Initial configurations that contains
2500, 4500 and 13824 molecules were generated at the calculated equilibrium
density. (3) NVT simulations with SPME electrostatic for system $%
S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$
were used as initial configurations for system $S_{1}$ and $M_{1}$,
respectively. The final configuration of $L_{1}^{\prime }$ was
used as initial configurations for system $L_{0}$ and $L_{1}$. % The SPME
% parameters for all simulations reported by this work is: real space
% cut-off 1.90~nm.
% [ {\color{blue} COMMENT: The following has been moved here, OK? If we need a
%   special care, please modify.}]
Using the density in the NVT simulation with
SPME electrostatic, the pressure ($-0.4\pm 1.5$~Bar) is reproducing the
target pressure of 1.0~Bar, which means the system is in desired
thermodynamic state.

@@

The smallest system $S_{1}$ was adopted for the quantities that are computed
by estimating fluctuations (in this work heat capacities, compressibility,
thermal expansion coefficient, dielectric constant, diffusion constant and
viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}%
), because simply increasing the size of the system does not
improve the accuracy of the simulation~\cite%
{milchev1986fluctuations,ferrenberg1991statistical}. The optimal way of
measuring these properties is to simulate with smaller systems 
% (as far as the finite size effect is negligible)
and run longer simulations for longer time-averages. The reason of using Nos%
\'{e}-Hoover thermostat is that it perturbs the dynamics of the system only
slightly, while the Langevin thermostat is likely to substantially change
the dynamics when the coupling is very strong, therefore, the former was
used in computing the dynamical properties like the diffusion constant and
viscosity. The quantities that are ensemble averages (in this work,
pressure, chemical potential, radial distribution function and Kirkwood-G
factor are of this type) were computed by the largest system $L_{0}$ or $L_{1}$, in order to
achieve higher parallel efficiency. The system $M_{1}$ is simulated to
investigate the size-dependency of the Kirkwood-G factor~\cite%
{vanderSpoel2006origin}.

@@

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors.
The dependence of the ZM results on the order\ $l$\ is \recheck{little}.
Although the splitting parameter, $\alpha $, also does not have significant
influence on almost all these thermodynamic quantities for $l=1$, only the
isothermal compressibility admits a weak dependence [\recheck{all except $\alpha=2$ are in the statistical uncertainty, by which we cannot say $\alpha=1$ is optimal... I remove ``and $\alpha=1$ seems optimal''}].
Overall, the ZM\ agrees with the SPME results without any bias and
out-performs the RF.

\recheck{
  It should be noticed that in the calculation of the chemical potential,
  the energy correction plays an important role. In the case of $l=1$, $\alpha = 0.0\,\text{nm}^{-1}$,
  it contributes $-0.1$~kJ/mol to the final result.
  By increasing $l$ or $\alpha$, this contribution
  becomes more significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha = 0.0\,\text{nm}^{-1}$, and
  $-1.0$~kJ/mol for $l=1$, $\alpha = 2.0\,\text{nm}^{-1}$, respectively.
}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level.
\recheck{This uncertainty is twice of the standard deviation of the estimates (which are averages along MD trajectories) that
is calculated by the block average method~\cite{janke2002statistical}.}
}
\label{fig:pres-comp}
\end{figure}

@@

The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
{fig:pres-l1}. The result of $\alpha =0.5\,$nm$^{-1}$ is similar to $\alpha
=0$ and shows good convergence. However, a higher $\alpha $ shifts the
pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1$
should be used in the simulations where the high accuracy in the pressure is
important. This "anti-damping effect" is similarly seen in the energy
accuracy in the TIP3P model~\cite{fukuda2014zero}.
% [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
In SI the results of the higher order are shown, which are similar to that
of $l=1$, but indicate less significant dependency on $\alpha $ for a large $%
l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
the pair potential of the ZM~\cite{fukuda2014zero}. The convergence is not sensitive to $%
\alpha $ up to $1.0\,\text{nm}^{-1}$.

\recheck{It should be noted that even with the system $L_0$ that contains 13824 water molecules}, the
fluctuation (measured by standard deviation) of the pressure is roughly
100~Bar, which means that it is very difficult to achieve very accurate
estimate for this quantity. In practice a pressure error of 20~Bar is still
acceptable.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
\caption{The dielectric constant convergence with respect to
  length of the trajectories used to compute the value.
  The SPME, ZM method $l=1$ to 4 and RF are presented.
  The cut-off distance of ZM and RF methods was 1.2~nm. The working parameters of SPME are given in Sec.~\ref{sec:protocols}
  The system used for simulation is $S_1$.
}
\label{fig:eps-conv}
\end{figure}

The dielectric constant computed by ZM method at different orders are listed
in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
In contrast, the RF method has poor accuracy in the dielectric constant.
It is
well known that the dielectric feature shows system-size dependence~\cite%
{vanderSpoel2006origin}, therefore we further investigated this dependence
and also the effect of the cutoff length, as shown in Table~I of SI. ZM shows
good results without any \recheck{system-size dependency} and indicate $r_{\text{c}}\sim
1.2\, $nm\ being suffice for the accuracy. Since a slow convergence is also known for
the dielectric constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv},
and confirm the sufficient convergence w.r.t.~the length of the trajectories.
\recheck{[COMMENT: the system size and cut-off dependency
  are important,
  but since the result are consistent with system $S_1$ and rc=1.2~nm (shown in table II),
  and NO new phenomenum is observed, 
  they are put in SI.]}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}\\
\includegraphics[]{fig/result.nvt/fig-gkr.eps} 
\caption{The Kirkwood G-factor calculated for system $%
M_{1}$ (a) and $L_{1} $ (b). ZM method of orders $l=1,2,3$ and 4 with the
cut-off 1.2~nm and splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$
are plotted. The RF method is shown as an comparison, which uses a cut-off
radius of 1.2~nm and dielectric constant of 80. The statistical uncertainty
of the SPME method is presented at 95~\% confidence level with the red error
bars. the statistical uncertainty of the SPME method is denoted by the red
error bars. The statistical uncertainties of the other methods are
essentially of the same size as the SPME, so they are not presented in the
figure for clarity.}
\label{fig:gkr}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-conv.eps} %
\caption{ The cut-off dependency in calculating the Kirkwood-G factor. The
order of ZM method is $l=3$. The splitting parameter is $\protect%
\alpha =0.0\,\text{nm}^{-1}$. The
statistical uncertainty is presented at 95~\% confidence level by the
error bars. }
\label{fig:gkr-conv}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps} %
\caption{ The splitting parameter dependency in calculating the Kirkwood-G factor at order $l=1$.
  The cut-off radius is 1.2~nm. The
statistical uncertainty is presented at 95~\% confidence level by the
error bars. }
\label{fig:gkr-damp-l1}
\end{figure}

We thus investigated the cut-off dependency in calculating the Kirkwood-G
factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$.
Without surprising, the Kirkwood-G factor converges to the SPME result
when using increasingly large cut-off radius.
\recheck{In Fig.~\ref{fig:gkr-damp-l1}, it shows that in the case of $l=1$, 
  the largest splitting parameter ($\alpha=2.0\ \textrm{nm}^{-1}$) is worse in calculating
  the Kirkwood-G factor than smaller splitting parameters.}
Splitting parameter dependency
was not so clear for $l=2$ and 3 (shown in SI).  Note that in many cases the discrepancies
from the SPME were relatively prominent in the middle range of the distance
and they tend small for larger distance.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis.eps}
\caption{The convergence
  of the integrated auto-correlation function $I_{\protect\eta }(T)$.
  Different orders of ZM method are compared with the SPME as well as RF results.
  The error bars indicating 95\% confidence level are plotted with the SPME
  method. }
\label{fig:conv-vis}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis-l1-damp.eps}
\caption{The convergence
  of the integrated auto-correlation function $I_{\protect\eta }(T)$.
  Different splitting parameters for ZM order $l=1$ are plotted.
The
error bars indicating 95\% confidence level are plotted with the SPME
method. }
\label{fig:conv-vis-damp}
\end{figure}

@@

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
) with $\alpha =0$\ and RF methods. It is observed from the figure
that the ZM RDFs are consist very well with the SPME RDF, except
oscillations around the cut-off radius. This oscillations are not so large,
as the maximum magnitude of the discrepancies from the SPME is about $2\%$, but should be artificial. However,
higher order ZM method present lower amplitude oscillation, and when $l\geq 3
$, the improvement is dramatic and the oscillation is almost negligible.

{\color{red} Shall we comment here on the fact that group cut-off produces
smoother RDF? Add figures in Supplementary material \bluec{ Do you
mean the reason of the goodness in RF?} \recheck{Yes, shall we discuss it? or it is too complicated and not very relavant to the current paper?}}

@@

In summary, ZM works well for almost all cases. Damping effect of the
splitting parameter, viz., larger $\alpha $\ gives accurate results, was
seen in several quantities. The weak effect is seen in the isothermal
compressibility, \recheck{Kirkwood-G factor (only $l=1$)} and dynamical quantities including the diffusion constant
and viscosity, while the strong effect is seen in the RDF. Anti-damping
effect was also observed in the pressure when $\alpha >1$. A larger order is
preferable slightly for dynamical quantities including diffusion constant
and viscosity, and significantly for the RDF. Whereas a smaller order is
preferable for the pressure, though $l=1,2$\ are similar.

>>>>

%2multibyte Version: 5.50.0.2952 CodePage: 932
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
%\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
% \input{tcilatex}

@@

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2952}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Tuesday, November 11, 2014 22:18:30}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}
\input{tcilatex}
\begin{document}

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\author{Haruki Nakamura}
\date{\today}

@@

{\color{red} If we want to discuss the issue of cut-off method, a short
introduction of the group cut-off v.s.~the atom cut-off method. (will
discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
do you mean? {\color{red} I mean the explanation of group and atomistic
cut-off method. the traditional gromacs uses gropu cut-off as default. We
need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
If we feel the resulted descriptions are too detailed, they will go to SI.}] 
}

@@

\subsection{Simulation protocols}

\label{sec:protocols} In this work, we focus on a system of water molecules
modeled by TIP3P~\cite{jorgensen1983comparison} point-charge particles. 
% Other point-charge water models differ in the modeling parameters, and
The accuracy of ZM method in other water models is out of the scope of the
current work. However, since the point-charge water models share similar
idea, and only differ in the model parameters, it is highly probable that ZM
works well with other water models if it works well with TIP3P.

@@

The neighbor lists were updated every 5 time-steps. The \textquotedblleft 
\texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used. In
order to mimic the atomistic cut-off manner, the radius for neighbor list
building was set 0.3~nm larger than the cut-off radius (the maximum of
Coulomb cut-off and the van der Waals cut-off). [ {\color{blue} COMMENT:
Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}] To
make sure the van der Waals interactions were cut-off in a smooth way, they
are modified in a shell of $0.05$~nm width near the cut-off sphere by the
Gromacs \textquotedblleft \texttt{shift}\textquotedblright\ method.

The short-range part of SPME method {\color{red} was cut-offed at 1.9~nm,
and was}[ {\color{blue} OK] }smoothed in a shell of $0.05$~nm width by the
Gromacs \textquotedblleft \texttt{pme-switch}\textquotedblright\ method. The
reciprocal space grid spacing was set to 0.06~nm, with B-Spline
interpolation order of 6. These parameters were chosen to be more accurate
than the Gromacs default choices (grid spacing 0.12~nm and interpolation
order 4). The splitting parameter was optimized by the error estimate for
the SPME method, which is implemented in Gromacs by tool \textquotedblleft 
\texttt{g\_pme\_error}\textquotedblright ~\cite{wang2010optimizing}. The
optimized real space and reciprocal space force computing errors were
equally distributed as $1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude
of the forces are of order $10^{2}$~kJ/(mol nm), this force computing
precision almost reaches the limit of the single-precision representation of
the floating point numbers. [ {\color{blue} COMMENT: Did you use the
conducting boundary conditions? (maybe it is default in gromacs.) Please
state the thing.}]

In the simulations of the RF method, the interactions were cut-off in the
group manner, so the radius for neighbor list building is set identical to
the cut-off radius. No cut-off smoothing of the electrostatic interaction
was applied in the cases of RF simulations. We used $1.2$~nm cut-off and the
experimental dielectric constant $\varepsilon _{\text{rf}}=80$.

The ZM method was implemented in Gromacs with the tabulated electrostatic
interaction. A home-made code was used to generate the interaction tables. {%
\color{blue} }$\bigstar $

@@

The initial configurations were prepared by in the following steps: (1) An
NPT simulation of system $L_{0}$ with SPME electrostatic was performed. The
equilibrium density (984.1~$\text{kg}/\text{m}^{3}$) of the system is
calculated from this simulation. (2) Initial configurations that contains
2500, 4500 and 13824 molecules were generated at the calculated equilibrium
density. (3) NVT simulations with SPME electrostatic for system $%
S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$ were
used as initial configurations for system $S_{1}$ and $M_{1}$, respectively.
The final configuration of $L_{1}^{\prime }$ was used as initial
configurations for system $L_{0}$ and $L_{1}$. % The SPME
% parameters for all simulations reported by this work is: real space
% cut-off 1.90~nm.
% [ {\color{blue} COMMENT: The following has been moved here, OK? If we need a
%   special care, please modify.}]
Using the density in the NVT simulation with SPME electrostatic, the
pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of 1.0~Bar,
which means the system is in desired thermodynamic state. [ {\color{blue}
COMMENT: If there are any specific conditions only for the pressure
calculation, please state around here or elsewhere.] }

@@

The smallest system $S_{1}$ was adopted for the quantities that are computed
by estimating fluctuations (in this work heat capacities, compressibility,
thermal expansion coefficient, dielectric constant, diffusion constant and
viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}%
), because simply increasing the size of the system does not improve the
accuracy of the simulation~\cite%
{milchev1986fluctuations,ferrenberg1991statistical}. The optimal way of
measuring these properties is to simulate with smaller systems 
% (as far as the finite size effect is negligible)
and run longer simulations for longer time-averages. The reason of using Nos%
\'{e}-Hoover thermostat is that it perturbs the dynamics of the system only
slightly, while the Langevin thermostat is likely to substantially change
the dynamics when the coupling is very strong, therefore, the former was
used in computing the dynamical properties like the diffusion constant and
viscosity. The quantities that are ensemble averages (in this work,
pressure, chemical potential, radial distribution function and Kirkwood-G
factor are of this type) were computed by the largest system $L_{0}$ or $%
L_{1}$, in order to achieve higher parallel efficiency. The system $M_{1}$
is simulated to investigate the size-dependency of the Kirkwood-G factor~%
\cite{vanderSpoel2006origin}.

@@

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors. The dependence of the ZM results on the order\ $l$\ is {\color{red}
little}. Although the splitting parameter, $\alpha $, also does not have
significant influence on almost all these thermodynamic quantities for $l=1$%
, only the isothermal compressibility admits a weak dependence [{\color{red}
all except $\alpha =2$ are in the statistical uncertainty, by which we
cannot say $\alpha =1$ is optimal... I remove \textquotedblleft and $\alpha
=1$ seems optimal\textquotedblright } {\color{blue} OK}]. Overall, the ZM\
agrees with the SPME results without any bias and out-performs the RF.

{\color{red} It should be noticed that in the calculation of the chemical
potential, the energy correction plays an important role. In the case of $%
l=1 $, $\alpha =0.0\,\text{nm}^{-1}$, it contributes $-0.1$~kJ/mol to the
final result. By increasing $l$ or $\alpha $, this contribution becomes more
significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha =0.0\,\text{nm}%
^{-1}$, and $-1.0$~kJ/mol for $l=1$, $\alpha =2.0\,\text{nm}^{-1}$,
respectively. [\color{blue}COMMENT: We will clarify what is the "energy
correction" after making SecII, and describe the relation to IPSp after
making Appendix B.] }

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.} }
\label{fig:pres-comp}
\end{figure}

@@

The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
{fig:pres-l1}. The result of $\alpha =0.5\,$nm$^{-1}$ is similar to $\alpha
=0$ and shows good convergence. However, a higher $\alpha $ shifts the
pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1$
should be used in the simulations where the high accuracy in the pressure is
important. This "anti-damping effect" is similarly seen in the energy
accuracy in the TIP3P model~\cite{fukuda2014zero}. 
% [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
In SI the results of the higher order are shown, which are similar to that
of $l=1$, but indicate less significant dependency on $\alpha $ for a large $%
l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
the pair potential of the ZM~\cite{fukuda2014zero}. The convergence is not
sensitive to $\alpha $ up to $1.0\,\text{nm}^{-1}$.

{\color{red} It should be noted that even with the system $L_{0}$ that
contains 13824 water molecules[} {\color{blue} OK}], the fluctuation
(measured by standard deviation) of the pressure is roughly 100~Bar, which
means that it is very difficult to achieve very accurate estimate for this
quantity. In practice a pressure error of 20~Bar is still acceptable.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
\caption{The dielectric constant convergence with respect to length of the
trajectories used to compute the value. The SPME, ZM method $l=1$ to 4 and
RF are presented. The cut-off distance of ZM and RF methods was 1.2~nm. The
working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
system used for simulation is $S_{1}$.[ {\color{blue} This is for $S_{1}$
and not shown in your report. right? }]}
\label{fig:eps-conv}
\end{figure}

The dielectric constant computed by ZM method at different orders are listed
in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
In contrast, the RF method has poor accuracy in the dielectric constant. It
is well known that the dielectric feature shows system-size dependence~\cite%
{vanderSpoel2006origin}, therefore we further investigated this dependence
and also the effect of the cutoff length, as shown in Table~I of SI. ZM
shows good results without any {\color{red} system-size dependency} {[} {%
\color{blue} OK}]and indicate $r_{\text{c}}\sim 1.2\,$nm\ being suffice for
the accuracy. Since a slow convergence is also known for the dielectric
constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv}%
, and confirm the sufficient convergence w.r.t.~the length of the
trajectories. {%
\color{red} [COMMENT: the system size and cut-off dependency
  are important,
  but since the result are consistent with system $S_1$ and rc=1.2~nm (shown in table II),
  and NO new phenomenum is observed, 
  they are put in SI.]\lbrack } {\color{blue} OK}]

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}\newline
\includegraphics[]{fig/result.nvt/fig-gkr.eps}
\caption{The Kirkwood G-factor calculated for system $M_{1}$ (a) and $L_{1} $
(b). ZM method of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and
splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$ are plotted. The
RF method is shown as an comparison, which uses a cut-off radius of 1.2~nm
and dielectric constant of 80. The statistical uncertainty of the SPME
method is presented at 95~\% confidence level with the red error bars. the
statistical uncertainty of the SPME method is denoted by the red error bars.
The statistical uncertainties of the other methods are essentially of the
same size as the SPME, so they are not presented in the figure for clarity.}
\label{fig:gkr}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
\caption{ The cut-off dependency in calculating the Kirkwood-G factor. The
order of ZM method is $l=3$. The splitting parameter is $\protect\alpha %
=0.0\,\text{nm}^{-1}$. The statistical uncertainty is presented at 95~\%
confidence level by the error bars. }
\label{fig:gkr-conv}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps}
\caption{ The splitting parameter dependency in calculating the Kirkwood-G
factor at order $l=1$. The cut-off radius is 1.2~nm. The statistical
uncertainty is presented at 95~\% confidence level by the error bars. [ {\ 
\color{blue} This is also not shown in your report. right? }]}
\label{fig:gkr-damp-l1}
\end{figure}

We thus investigated the cut-off dependency in calculating the Kirkwood-G
factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$%
. Without surprising, the Kirkwood-G factor converges to the SPME result
when using increasingly large cut-off radius. {\color{red} In Fig.~\ref%
{fig:gkr-damp-l1}, it shows that in the case of $l=1$, the largest splitting
parameter ($\alpha =2.0\ \text{nm}^{-1}$) is worse in calculating the
Kirkwood-G factor than smaller splitting parameters.[} {\color{blue} OK}]
Splitting parameter dependency was not so clear for $l=2$ and 3 (shown in
SI). Note that in many cases the discrepancies from the SPME were relatively
prominent in the middle range of the distance and they tend small for larger
distance.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis.eps}
\caption{The convergence of the integrated auto-correlation function $I_{%
\protect\eta }(T)$. Different orders of ZM method are compared with the SPME
as well as RF results. The error bars indicating 95\% confidence level are
plotted with the SPME method. }
\label{fig:conv-vis}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis-l1-damp.eps}
\caption{The convergence of the integrated auto-correlation function $I_{%
\protect\eta }(T)$. Different splitting parameters for ZM order $l=1$ are
plotted. The error bars indicating 95\% confidence level are plotted with
the SPME method. }
\label{fig:conv-vis-damp}
\end{figure}

@@

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
) with $\alpha =0$\ and RF methods. It is observed from the figure that the
ZM RDFs are consist very well with the SPME RDF, except oscillations around
the cut-off radius. This oscillations are not so large, as the maximum
magnitude of the discrepancies from the SPME is about $2\%$,{[} {\color{blue}
"$2\%"$ is just my guess. How about stating here the maximum error for
individual $l$}] but should be artificial. However, higher order ZM method
present lower amplitude oscillation, and when $l\geq 3$, the improvement is
dramatic and the oscillation is almost negligible.

{\color{red} Shall we comment here on the fact that group cut-off produces
smoother RDF? Add figures in Supplementary material {\color{blue} Do you
mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
it? or it is too complicated and not very relevant to the current paper?}[} {%
\color{blue} It is preferable to write it if the reason of the goodness is
clear. Anyway, please describe.... This is the only matter ZM is inferior to
RF. So, it may be interesting if the reason is clear. }]

@@

In summary, ZM works well for almost all cases. Damping effect of the
splitting parameter, viz., larger $\alpha $\ gives accurate results, was
seen in several quantities. The weak effect is seen in the isothermal
compressibility, {\color{red} } and dynamical quantities including the
diffusion constant and viscosity, while the strong effect is seen in the
RDF. Anti-damping effect was also observed in the pressure when $\alpha >1$
and  {\color{blue}Kirkwood-G factor (only $l=1$).[ OK??}] A larger order is
preferable slightly for dynamical quantities including diffusion constant
and viscosity, and significantly for the RDF. Whereas a smaller order is
preferable for the pressure, though $l=1,2$\ are similar.
